Run aquaculture model for Atlantic salmon

### 2025-08-01 06_run_atlantic_salmon_model.qmd
Minor adj

# Check that the feed will actually work
targets::tar_make(test_reference_feed)
targets::tar_load(test_reference_feed)
test_reference_feed # should be ~1430 g, or really anything other than 0

# Get harvest sizes for all farms
targets::tar_make(names = c("harvest_size", "feed_params"))
targets::tar_load(harvest_size)

@@

# Pre-run to reduce load
targets::tar_make(
  names = !c("farm_run", "cohort_results", "biomass_produced", "farm_results"), 
  seconds_meta_append = 90,
  callr_function = NULL
)

# Run results
targets::tar_make(
  names = c("farm_run", "cohort_results", "biomass_produced", "farm_results"), 
  seconds_meta_append = 90,
  shortcut = T,
  callr_function = NULL
)

@@

targets::tar_load(stat_names)
targets::tar_load(farm_IDs)
targets::tar_load(feed_names)

print("Loading farm results...")
targets::tar_load(farm_results)
for (stat_name in stat_names) {
  farm_results %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
}
rm(farm_results)

>>>>

# Check that the feed will actually work
targets::tar_make(test_reference_feed)
targets::tar_load(test_reference_feed)
test_reference_feed # if weight = 0 then the feeds aren't processing properly

# Get harvest sizes for all farms
targets::tar_make(names = contains(c("harvest_size", "feed_params")))
targets::tar_load(harvest_size_chunked)
harvest_size <- harvest_size_chunked %>% bind_rows()

@@

# Pre-run to reduce load
targets::tar_make(
  names = c("farm_IDs_chunked", "farm_ts_data_chunked", "farm_IDs", "test_reference_feed", "farm_temp_data_chunked", "harvest_size_chunked", "farm_static_data_chunked"), 
  seconds_meta_append = 90#, callr_function = NULL
)

# Run results
targets::tar_make(
  names = c("farm_run_chunked", "stat_names", "farm_results_chunked", "biomass_produced_chunked", "cohort_results_chunked" ), 
  seconds_meta_append = 90,
  shortcut = T
)

@@

targets::tar_load(stat_names)
targets::tar_load(farm_IDs_chunked) %>% unlist()
targets::tar_load(feed_names)

print("Loading farm results...")
targets::tar_load(farm_results_chunked)
for (stat_name in stat_names) {
  farm_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
}
rm(farm_results)
